Think deep for reef resilience

### 2025-08-07 paper/paper_draft.qmd
Expand on DHW section and other small changes
Mark where citation of repository is needed for extra GCM results. Add conclusion paragraph heading.

Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology
[@liu2017; @skirving2020]. For each pixel of SST data, the monthly mean SST climatology (MM)
was calculated as the mean SST for each month over 1985 to 2012, adjusted to centre at year
1988.2857 (see Skirving et al. [-@skirving2020]). The "HotSpot SST Anomaly" [@skirving2020]
was calculated as the difference between daily SST values and the maxmimum of a pixel's MM
climatology (maximum monthly mean). DHW values are then calculated as the 12-week rolling
sum of positive HotSpot SST Anomaly values for a pixel. **\[TI: Could you confirm the above
is described correctly?\]**

@@

| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Individual results displayed |
|-----------------------|-----------------------|-----------------------|-----------------------|
| EC-Earth3-Veg | 4.31 | High | Supplementary |
| ACCESS-CM2 | 4.72 | High | Supplementary |
| ACCESS-ESM1-5 | 3.87 | Intermediate | Main text |
| GFDL-CM4 | 2.9 | Low | Supplementary |
| NorESM2-MM | 2.5 | Low | Supplementary |

@@

>>>>

Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology
[@liu2017; @skirving2020]. For each pixel of SST data, the monthly mean SST climatology (MM)
was calculated as the mean SST for each month over 1985 to 2012, adjusted to centre at year
1988.2857 (see Skirving et al. [-@skirving2020]). The "HotSpot SST Anomaly" [@skirving2020]
was calculated as the difference between daily SST values and the maxmimum of a pixel's MM
climatology (maximum monthly mean). DHW values were then calculated as the 12-week rolling
sum of positive HotSpot SST Anomaly values for a pixel. Within each year the maximum of
monthly mean DHW values was calculated. Reef scale DHW timeseries were extracted by taking
the average DHW level over pixels touching a reef.

@@

| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Individual results displayed |
|-----------------------|-----------------------|-----------------------|-----------------------|
| EC-Earth3-Veg | 4.31 | High | **insert repo citation** |
| ACCESS-CM2 | 4.72 | High | **insert repo citation** |
| ACCESS-ESM1-5 | 3.87 | Intermediate | Main text |
| GFDL-CM4 | 2.9 | Low | **insert repo citation** |
| NorESM2-MM | 2.5 | Low | **insert repo citation** |

@@

# Conclusion
